### 2017-12-10 readme.rmd
added press release quote

>>>>

And from a press release *[In the beginning there was the sponge](http://www.en.uni-muenchen.de/news/newsarchiv/2017/woerheide_schwammanalysen.html)* describing their new paper:

> ... their results are unequivocal: The sponges form the earliest branch on the animals' family tree... "Our results confirm the classical assumptions concerning early animal evolution, and should help to put an end to the recent controversy over the origin of multicellular animals," Wörheide concludes.
